Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-11-27 paper/paper.tex
add suppfiles per _PLoS Pathogens_ editorial staff request

\begin{suppfile}
\caption{{\bf Sequences of the IFN reporters in \FIG{IFNrare}A.}
See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/IFN_stochastic/IFN_reporter/plasmids}.
}
\label{suppfile:reporter_sequences}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf Genbank files giving sequences of the wild-type and synonymously barcoded viruses}.
See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn.gb} and \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn-double-syn.gb}.}
\label{suppfile:virus_seqs}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf A text file giving the primers used to amplify the influenza cDNAs for PacBio sequencing.}
See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/WorkflowSchematic/PacBio_primer_list.txt} 
}
\label{suppfile:primer_sequences}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf A CSV file giving the genotypes in \FIG{genotypes}.}
See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/paper/figures/single_cell_figures/genotypes.csv}.}
\label{suppfile:genotypes}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf A CSV file giving the viral mutations and related information in \FIG{mutations}.}
See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/paper/figures/single_cell_figures/mutations.csv}.}
\label{suppfile:mutations}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf Genbank plasmid maps for the mutant genes cloned into the pHW* bi-directional reverse genetics plasmid~\cite{hoffmann2000dna}.}
See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/FluVariantPlasmidMaps}}
\label{suppfile:validation_sequences}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:pacbio_analysis}
{\bf HTML rendering of Jupyter notebook that analyzes the PacBio data.}
See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/raw/master/paper/figures/pacbio_single_cell_figures/pacbio_analysis.html}.
The actual Jupyter notebook is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/pacbio_analysis.ipynb}.}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:monocle_analysis}
{\bf HTML rendering of Jupyter notebook that analyzes the annotated cell-gene matrix.}
See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/raw/master/paper/figures/single_cell_figures/monocle_analysis.html}.
The actual Jupyter notebook is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/monocle_analysis.ipynb}.}
\end{suppfile}

>>>>

\begin{suppfile}
\caption{{\bf Sequences of the IFN reporters in \FIG{IFNrare}A.}
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/IFN_stochastic/IFN_reporter/plasmids}.
}
\label{suppfile:reporter_sequences}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf Genbank files giving sequences of the wild-type and synonymously barcoded viruses}.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn.gb} and \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn-double-syn.gb}.
}
\label{suppfile:virus_seqs}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf A text file giving the primers used to amplify the influenza cDNAs for PacBio sequencing.}
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/WorkflowSchematic/PacBio_primer_list.txt} 
}
\label{suppfile:primer_sequences}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf A CSV file giving the genotypes in \FIG{genotypes}.}
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/paper/figures/single_cell_figures/genotypes.csv}.
}
\label{suppfile:genotypes}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf A CSV file giving the viral mutations and related information in \FIG{mutations}.}
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/paper/figures/single_cell_figures/mutations.csv}.
}
\label{suppfile:mutations}
\end{suppfile}

\begin{suppfile}
\caption{
{\bf Genbank plasmid maps for the mutant genes cloned into the pHW* bi-directional reverse genetics plasmid~\cite{hoffmann2000dna}.}
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/FluVariantPlasmidMaps}
}
\label{suppfile:validation_sequences}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:pacbio_analysis}
{\bf HTML rendering of Jupyter notebook that analyzes the PacBio data.}
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/raw/master/paper/figures/pacbio_single_cell_figures/pacbio_analysis.html}.
The actual Jupyter notebook is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/pacbio_analysis.ipynb}.
}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:monocle_analysis}
{\bf HTML rendering of Jupyter notebook that analyzes the annotated cell-gene matrix.}
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/raw/master/paper/figures/single_cell_figures/monocle_analysis.html}.
The actual Jupyter notebook is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/monocle_analysis.ipynb}.
}
\end{suppfile}
